Data Preparation

### 2019-02-27 Data Preparation.Rmd
use list to manipulate textual data (instead of multiple dataframes)

```{r setup, include = T}
knitr::opts_chunk$set(cache.path = "Cache/Data Preparation/")
```

@@

## Setup
First, we import the spreadsheet with information pertraining the Aims of the Degree (AoD) and Assessments from the drive and save it under `lists_brut`. ` lists_brut` contains 4 columns, under which we find the `19` types of assessment, the `18` aims of the degree (AoD) of the degree, and  two columns containing binary vectors indicating which assessment types and AoD  we will consider when ploting the data[^1].
Then we create a list with this same columns, but instead of having binary vectors for the plots, we keep vectors of only the names of relevant assessments and AoDs for the plots (`Assessment_plot`adnd `AoD_plot` respectively). We also any imported emtpy cells.
```{r import list}
lists_brut <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1239912347')
lists <- list(
  Assessment      = lists_brut$Assessment,
  Assessment_plot = lists_brut$Assessment[lists_brut$`Assessment for Plot` == 1],
  AoD             = lists_brut$Aim[!is.na(lists_brut$Aim)],
  AoD_plot        = lists_brut$Aim[lists_brut$`Aim for Plot`[!is.na(lists_brut$Aim)] == 1]
  )
rm(lists_brut)
```

@@

```{r import d_course d_assessment and d_ILO, cache = TRUE}
d_course <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1655700848')
print(d_course)

d_assessment <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1102665750') %>%
  select(- `Comment on Assessment`) %>%
  gather(Assessment, assessment_covered, - `Course ID`, factor_key = T) %>%
  filter(assessment_covered == 1) %>%
  select(- assessment_covered) %>%
  arrange(`Course ID`)
print(d_assessment)

d_ILO <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1896457050') %>%
  select(- c(Comments, Comments_for_Jeroen)) %>%
  gather(AoD, AoD_covered, -c(`Course ID`, Objectives), factor_key = T) %>%
  filter(AoD_covered == 1) %>%
  select(- AoD_covered) %>%
  rename(ILO = Objectives) %>%
  arrange(`Course ID`)
print(d_ILO)
```

## Textual Data
### Course Catalogues
In order to conduct a preliminary topic modeling of course content, we first analyze their description in the course catalogues. The corpus `corpus_catalogues` contains the pdfs of the `5` most recent course catalogues.
```{r import corpus_catalogues, cache = TRUE}
corpus_catalogues <- Corpus(x             = DirSource("./Input/Catalogues"),
                            readerControl = list(reader = readPDF(control = list(text = "-layout"))))
```

@@

```{r import corpus_manuals, cache = TRUE}
corpus_manuals <- Corpus(x             = DirSource("./Input/Manuals 2017-18"),
                         readerControl = list(reader = readPDF(control = list(text = "-layout"))))
```
## Student Data
The tibble `d_transcript` contains the transcript information of students as was provided. It has 40 columns, and rows correspond to a type of grade (e.g. final grade, attendance) per student per course per time they took it.

```{r import d_transcript, cache = TRUE}
d_transcript <- rbind(
  read_csv(
    "./Input/Raw Grades/grades1.csv",
    col_types = cols(
      `Program (Abbreviation)` = col_character(),
      `Appraisal Status` = col_character(),
      `Module Booking Reason (Description)` = col_character(),
      `Object name` = col_character(),
      `Start date` = col_character(),
      `End Date` = col_character()
      )
    ),

  read_csv(
    "./Input/Raw Grades/grades2.csv",
    col_types = cols(
      `Program (Abbreviation)` = col_character(),
      `Appraisal Status` = col_character(),
      `Module Booking Reason (Description)` = col_character(), 
      `Object name` = col_character(), 
      `Start date` = col_character(), 
      `End Date` = col_character()
      )
    )

@@

In order to determine which AoD each course covers with its ILOs, we first eliminate the AoD that are not covered by the ILOs, and then we keep only one instance of each combination of course and AoD in case a course had several ILOs covering the same AoD.
```{r d_AoD_ILO}
d_AoD_ILO <- distinct(d_ILO, `Course ID`, AoD)
print(d_AoD_ILO)
```

@@

```{r map_assessment_AoD}
map_assessment_AoD <- as.matrix(gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=719531216')[,lists$AoD] %>%
                                  mutate_all(as.logical))
rownames(map_assessment_AoD) <- lists$Assessment

# Print section of matrix
print(map_assessment_AoD[1:5, 8:12])
```

Now that we have the matrix `map_assessment_AoD`, we want to find out which AoDs are covered by a course through its assessments. To do this we create an empty tibble `d_AoD_assessment` to store which assessment is covered by each course, and which AoD said assessment covers.Then, we fill in the information with a loop.
In the loop, we first extract a row of `d_assessment` and save it as `observation`. Then, we determine the corresponding assessment which we save as `assessment`. Then, we use the matrix `map_assessment_AoD` to determine which AoD `assessment` covers and use `cbind` and `rbind` to add the information to the tibble `d_AoD_assessment`.
```{r d_AoD_assessment}
d_AoD_assessment <- tibble(`Course ID` = character(0),
                           Assessment  = character(0),
                           AoD         = character(0))

for(i in 1 : nrow(d_assessment)){

  observation <- d_assessment[i, ]

  assessments <- observation$Assessment
  AoD_covered <- map_assessment_AoD[assessments, ]
  AoD         <- lists$AoD[AoD_covered]

  if(length(AoD) >= 1) d_AoD_assessment <- rbind(d_AoD_assessment,
                                                 as_tibble(cbind(observation,
                                                                 AoD)))
}
rm(map_assessment_AoD, observation, AoD, AoD_covered, assessments, i)
```

Next, we keep ony one copy of each distinct combination of course and AoD in case a course had several assessments covering the same AoD (this is analogous to what we did with the tibble `d_AoD_ILO`).
```{r d_AoD_assessment distinct}
d_AoD_assessment <- distinct(d_AoD_assessment, `Course ID`, AoD)
print(d_AoD_assessment)
```

#### Combining AoD from ILOs and from assessments
Finally, we can use a `rbind` to combine the two tibbles `d_AoD_ILO` and `d_AoD_assessment`. We also use `distinct` in case a course covers an AoD with both its ILOS and its assessments.
```{r rbind d_AoD_ILO and d_AoD_assessment}
d_AoD <- rbind(d_AoD_ILO,
               d_AoD_assessment) %>%
  distinct %>%
  arrange(`Course ID`)

rm(d_AoD_ILO, d_AoD_assessment)
print(d_AoD)
```

@@

Now that we have a clear overview of the distribution of AoDs (`d_AoD`) and assessments (`d_assessment`) among the courses, let us add variables to the tibble `d_course` that contain the information at the course level. For this we create the following three tibbles:
1) `d_ILO_detail` contains two columns indicating the code of the course and the number of ILOs it contains.
2) `d_assessment_detail` contains three columns indicating the code of the course, the number of assessments it covers and a list of the assessments it covers. 
3) `d_AoD_detail` contains three columns indicating the code of the course, the number of AoD it covers and a list of the AoD it covers. 
Then we use a `full_join` to add these variables to the tibble `d_course`.
```{r d_course detail}
d_ILO_detail <- d_ILO %>% 
  distinct(`Course ID`, ILO) %>%
  count(`Course ID`) %>%
  rename(n_ILO = n)

d_assessment_detail <- d_assessment %>%
  group_by(`Course ID`) %>%
  summarise(n_assessment = n(),
            `Assessments Covered` = paste(Assessment, collapse = ", "))

d_AoD_detail <- d_AoD %>%
  group_by(`Course ID`) %>%
  summarise(n_AoD = n(),
            `AoD Covered` = paste(AoD, collapse = ", "))

d_course_detail <- d_ILO_detail %>%
  full_join(d_assessment_detail, by = "Course ID") %>%
  full_join(d_AoD_detail       , by = "Course ID")

rm(d_ILO_detail, d_assessment_detail, d_AoD_detail)
print(d_course_detail)
```

```{r join d_course_detail}
d_course <- d_course %>%
  full_join(d_course_detail, by = "Course ID") %>%
  select(`Course ID`, `Course Title`, Cluster,
         n_ILO,
         n_assessment, `Assessments Covered`,
         n_AoD, `AoD Covered`, 
         everything())

rm(d_course_detail)
print(d_course)
```

The undegraduate research courses (*UGR-*) are only present at the `3000` level (advanced level). Yet, these course are also offered at the `2000` level (intermediate level). We use an `rbind` to duplicate the rows of the course `UGR3000` and mutate their `Code` to `UGR2000`.
```{r create UGR2000}
d_course <- d_course %>%
  rbind(filter(., `Course ID` %in% c("UGR3001", "UGR3002", "UGR3003", "UGR3005")) %>%
          mutate(`Course ID` = case_when(`Course ID` == "UGR3001" ~ "UGR2001",
                                  `Course ID` == "UGR3002" ~ "UGR2002",
                                  `Course ID` == "UGR3003" ~ "UGR2003",
                                  `Course ID` == "UGR3005" ~ "UGR2005")))

print(filter(d_course, `Course ID` %in% c("UGR2001", "UGR2002", "UGR2003", "UGR2005",
                                          "UGR3001", "UGR3002", "UGR3003", "UGR3005")))
```

Finally, we add a series of informative variable at the course level.
```{r d_course additional info}
d_course <- d_course %>%
  mutate(
    Letters = substring(`Course ID`, 1, 3),
    Number  = as.numeric(substring(`Course ID`, 4, 7)),
    Level   = case_when(between(Number, 1000, 1999) ~ "Introductory",
                        between(Number, 2000, 2999) ~ "Intermediate",
                        between(Number, 3000, 3999) ~ "Advanced"    ))

print(select(d_course, `Course ID`, Letters, Number, Level))
```

@@

```{r extracting overview, cache = TRUE}
# Setup
n_catalogue <- length(corpus_catalogues)
academic_years <- c("2014-2015", "2015-2016", "2016-2017", "2017-2018", "2018-2019")
d_description <- tibble(`Course ID`     = character(0),
                        `Academic Year` = character(0),
                        Overview        = character(0),
                        Description     = NA)

course_code <- c("COR", "HUM", "SCI", "SSC", "SKI", "PRO", "UGR", "CAP") %>%
  paste(collapse = "|")

content_to_exclude <- c(
  "^Core Courses \\(COR\\)",
  "^Humanities \\(HUM\\)",
  "^Sciences \\(SCI\\)",
  "^Social Sciences \\(SSC\\)",
  "^Skills Trainings \\(SKI\\)", "^Skills Training \\(SKI\\)",
  "^Project \\(PRO\\)", "^Projects \\(PRO\\)",
  "^Undergraduate Research \\(UGR\\)",
  " UCM Undergraduate\r\nResearch", "UCM Undergraduate\r\n  Research"
  ) %>%
  paste(collapse = "|")

# Loop 1
for(n in 1 : n_catalogue){

  cat <- content(corpus_catalogues[[n]])

  # Overview section in catalogue
  page_overview_start <- grep(pattern = "^Core Courses \\(COR\\)", x = cat) + 1
  page_overview_end   <- grep(pattern = "Appendix", x = cat) - 1
    if(length(page_overview_end) == 0) page_overview_end <- length(cat)
  cat_overview <- cat[page_overview_start : page_overview_end]

  # Course description only
  pages_to_exclude <- grep(pattern = content_to_exclude, x = cat_overview)
  cat_overview <- cat_overview[! 1 : length(cat_overview) %in% pages_to_exclude]

  # First pages of course overviews
  first_three_letters <- substr(cat_overview, start = 1, stop = 3)
  first_pages_overview <- grep(pattern = course_code, x = first_three_letters)

  # Loop 2
  for(page in first_pages_overview){

    # Extract description
    overview <- if((page + 1) %in% first_pages_overview) cat_overview[page]
                else paste(cat_overview[page : (page + 1)], collapse = " ")

    # Save overview
    code <- substr(overview, start = 1, stop = 7)
    year <- academic_years[n]
    d_description <- d_description %>%
      add_row(
        `Course ID` = code,
        `Academic Year` = year,
        Overview = overview,
        Description = NA
      )

  } # close for-loop (page)

} # close for-loop (n)

rm(corpus_catalogues,
   n_catalogue, academic_years, course_code, content_to_exclude,
   n, cat,
   page_overview_start, page_overview_end,
   pages_to_exclude, cat_overview,
   first_three_letters, first_pages_overview,
   page, overview, code, year)
print(d_description)
```

##### Extracting Descriptions

```{r extracting description, cache = TRUE}

@@

Since we want to use tools from dplyr and tidytext we must first transform our corpus into a dataframe.
```{r d_manual}
d_manual <- tidy(corpus_manuals) %>%
  select(id, text) %>%
  mutate(`Course ID` = substring(id, 1, 7)) %>%
  select(-id) %>%
  rename(Manual = text)

rm(corpus_manuals)
print(d_manual)
```

@@

To put everything into tidy text format, we first create three tibbles `d_overview_tidy`, `d_description_tidy`, `d_manual` that respectively store the overviews, descriptions and text from manuals in the tidy text format, with one row per course-year-word (and course-word for `d_manual`).
```{r tidy d_description}
d_overview <- d_description %>%
  select(`Course ID`, `Academic Year`, Overview) %>%
  unnest_tokens(output = word, input = Overview)

d_description <- d_description %>%
  select(`Course ID`, `Academic Year`, Description) %>%
  unnest_tokens(output = word, input = Description)

d_manual <- unnest_tokens(d_manual, output = word, input = Manual)
```

@@

We first create a function `stem_hunspell` which, given a term, returns its most basic stem (the last one from the list of stem returned by `hunspell_stem`). We would like to apply `stem_hunspell` on the words of `d_overview_tidy` and `d_manual`, since they have similar structures, we row bind them into `dictionary` to ease the application of `stem_hunspell`. However, since, `stem_hunspell` is not a vectorized function and the number of words in `dictionary` is large, we first use distinct on the `word` variable to find a list containing *once* each term present in the course overviews and manuals. Then, we use `mutate` to apply the function `stem_hunspell` on each word from our dictionary and save its results as a new column `word_stem`.
```{r stemming dictionary, cache = TRUE}
stem_hunspell <- function(term) {
  stems   <- hunspell_stem(term)[[1]] # look up the term in the dictionary
  n_stems <- length(stems)            # number of stems
  if (n_stems == 0) term              # if no stems, return original term
  else              stems[[n_stems]]  # if multiple stems, return last (most basic) stem
}

dictionary <- select(d_overview, `Course ID`, word) %>%
  rbind(d_manual) %>% 
  distinct(word) %>%
  mutate(word_stem = purrr::map_chr(.x = word,
                                    .f = stem_hunspell))

@@

Then, we use `stem_with_dictionary` to include the stems of all words in `d_description`, `d_overview`, and `d_manual`.
```{r stemming data sets}
stem_with_dictionary <- function(data) data %>%
                                         left_join(dictionary, by = "word") %>%
                                         rename(word_original = word,
                                                word = word_stem)

d_description <- stem_with_dictionary(d_description)
d_overview <- stem_with_dictionary(d_overview)
d_manual <- stem_with_dictionary(d_manual)

rm(stem_hunspell, stem_with_dictionary)
print(d_description) # See starting - start
```

### Removing Stopwords
Finally, we want to filter out some uninformative words from our textual data. For this, we first store all the unwanted words in a vector `sw_owm`. We also create function `remove_sw` which receives a dataframe as input and filters out all words in `sw_own`. Then we apply this function to `d_description`, `d_overview`, and `d_manual`.
```{r}
# Own stop words
sw_own <- c("______________________________________________________________________________",
            as.character(1:10))

remove_sw <- function(data) data %>%
  filter(! word %in% c(stop_words$word, sw_own))

d_description <- remove_sw(d_description)
d_overview <- remove_sw(d_overview)
d_manual <- remove_sw(d_manual)

rm(sw_own, remove_sw)
print(d_description) # stop words (on, the, of, etc, are excluded)
```

@@

# Save Data
```{r}
save(d_course, d_transcript,
     file = "Output/data_pillar_1.RDATA")
save(lists, d_course, d_AoD, d_assessment, d_transcript,
     d_overview, d_description, d_manual,
     file = "Output/data_pillar_2.RDATA")
```

>>>>

```{r setup, include = FALSE}
knitr::opts_chunk$set(cache.path = "Cache/Data Preparation/")
```

@@

## Setup
First, we import the spreadsheet with information pertraining the Aims of the Degree (AoD) and Assessments from the drive and save it under `lists_brut`. ` lists_brut` contains 4 columns, under which we find the `19` types of assessment, the `18` aims of the degree (AoD) of the degree, and  two columns containing binary vectors indicating which assessment types and AoD  we will consider when ploting the data[^1].
Then we create a list with this same columns, but instead of having binary vectors for the plots, we keep vectors of only the names of relevant assessments and AoDs for the plots (`Assessment_plot`adnd `AoD_plot` respectively). We also any imported emtpy cells.
```{r import list}
lists_brut <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1239912347') %>%
  map(na.omit)

lists <- list()

lists$Assessment      <- lists_brut$Assessment
lists$AoD             <- lists_brut$Aim

# selection of most important types of assessment an AoD to keep plots clear
lists$Assessment_plot <- lists$Assessment[lists_brut$`Assessment for Plot` == 1]
lists$AoD_plot        <- lists$AoD       [lists_brut$`Aim for Plot`        == 1]

rm(lists_brut)
```

@@

```{r import d_course d_assessment and d_ILO, cache = TRUE}
d_course <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1655700848') %>%
  print

d_assessment <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1102665750') %>%
  mutate_if(
    .predicate = is.numeric,
    as.logical
    ) %>%
  gather(
    key   = Assessment, 
    value = assessment_covered,
    Paper : Participation
    ) %>%
  filter(
    assessment_covered
    ) %>%
  select(
    - c(assessment_covered, `Comment on Assessment`)
    ) %>%
  arrange(
    `Course ID`
    ) %>%
  print

d_ILO <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1896457050')

d_AoD_ILO <- d_ILO %>%
  rename(
    ILO = Objectives
    ) %>%
  mutate_if(
    .predicate = is.numeric,
    as.logical
    ) %>%
  gather(
    key   = AoD, 
    value = AoD_covered,
    `Matrix Complete` : `Intercultural Skills`
    ) %>%
  filter(
    AoD_covered
    ) %>%
  select(
    - c(AoD_covered, Comments, Comments_for_Jeroen)
    ) %>%
  print
```

## Textual Data
### Course Catalogues
In order to conduct a preliminary topic modeling of course content, we first analyze their description in the course catalogues. The corpus `corpus_catalogues` contains the pdfs of the `5` most recent course catalogues.
```{r import corpus_catalogues, cache = TRUE}
d_text <- list()

d_text$catalogues <- Corpus(
  x             = DirSource("./Input/Catalogues"),
  readerControl = list(reader = readPDF(control = list(text = "-layout")))
  )
```

@@

```{r import corpus_manuals, cache = TRUE}
d_text$manuals <- Corpus(
  x             = DirSource("./Input/Manuals 2017-18"),
  readerControl = list(reader = readPDF(control = list(text = "-layout")))
  )
```

## Student Data
The tibble `d_transcript` contains the transcript information of students as was provided. It has 40 columns, and rows correspond to a type of grade (e.g. final grade, attendance) per student per course per time they took it.

```{r import d_transcript, cache = TRUE}
d_transcript1 <- read_csv(
  file = "Input/Raw Grades/grades1.csv",
  col_types = cols(
    `Program (Abbreviation)`              = "c",
    `Appraisal Status`                    = "c",
    `Module Booking Reason (Description)` = "c"
    )
  )

d_transcript2 <- read_csv(
  file = "Input/Raw Grades/grades2.csv",
  col_types = cols(
    `Program (Abbreviation)`              = "c",
    `Appraisal Status`                    = "c",
      `Object name`                       = "c",
      `Start date`                        = "c",
      `End Date`                          = "c"
    )
  )

d_transcript <- rbind(d_transcript1, d_transcript2)

rm(d_transcript1, d_transcript2)
```

@@

In order to determine which AoD each course covers with its ILOs, we first eliminate the AoD that are not covered by the ILOs, and then we keep only one instance of each combination of course and AoD in case a course had several ILOs covering the same AoD.
```{r d_AoD_ILO}
d_AoD_ILO
```

@@

```{r map_assessment_AoD}
map_assessment_AoD <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=719531216') %>%
  mutate_if(
    .predicate = is.numeric,
    .f         = as.logical
    ) %>%
  gather(
    key   = AoD, 
    value = AoD_covered,
    `Matrix Complete` : `Intercultural Skills`
    ) %>%
  filter(
    AoD_covered
    ) %>%
  select(
    - AoD_covered
    ) %>%
  arrange(
    Assessment
  ) %>%
  print
```

Now that we have the matrix `map_assessment_AoD`, we want to find out which AoDs are covered by a course through its assessments. To do this we create an empty tibble `d_AoD_assessment` to store which assessment is covered by each course, and which AoD said assessment covers.Then, we fill in the information with a loop.
In the loop, we first extract a row of `d_assessment` and save it as `observation`. Then, we determine the corresponding assessment which we save as `assessment`. Then, we use the matrix `map_assessment_AoD` to determine which AoD `assessment` covers and use `cbind` and `rbind` to add the information to the tibble `d_AoD_assessment`.
```{r d_AoD_assessment}
d_AoD_assessment <- d_assessment %>%
  left_join(
    map_assessment_AoD,
    by = "Assessment"
    ) %>%
  print

rm(map_assessment_AoD)
```

#### Combining AoD from ILOs and from assessments
Finally, we can use a `rbind` to combine the two tibbles `d_AoD_ILO` and `d_AoD_assessment`. We also use `distinct` in case a course covers an AoD with both its ILOS and its assessments.
```{r rbind d_AoD_ILO and d_AoD_assessment}
d_AoD <- rbind(
  d_AoD_ILO        %>% select(`Course ID`, AoD),
  d_AoD_assessment %>% select(`Course ID`, AoD)
  ) %>%
  distinct %>%
  arrange(
    `Course ID`
    ) %>%
  print

rm(d_AoD_assessment, d_AoD_ILO)
```

@@

Now that we have a clear overview of the distribution of AoDs (`d_AoD`) and assessments (`d_assessment`) among the courses, let us add variables to the tibble `d_course` that contain the information at the course level. For this we create the following three tibbles:
1) `d_ILO_detail` contains two columns indicating the code of the course and the number of ILOs it contains.
2) `d_assessment_detail` contains three columns indicating the code of the course, the number of assessments it covers and a list of the assessments it covers. 
3) `d_AoD_detail` contains three columns indicating the code of the course, the number of AoD it covers and a list of the AoD it covers. 
Then we use a `full_join` to add these variables to the tibble `d_course`.
```{r d_course detail}
d_ILO_detail <- d_ILO %>%
  count(
    `Course ID`, 
    sort = TRUE
    ) %>%
  rename(
    n_ILO = n
    ) %>%
  print

d_assessment_detail <- d_assessment %>%
  group_by(
    `Course ID`
    ) %>%
  summarise(
    n_assessment = n(),
    `Assessments Covered` = paste(Assessment, collapse = ", ")
    ) %>%
  print

d_AoD_detail <- d_AoD %>%
  group_by(
    `Course ID`
    ) %>%
  summarise(
    n_AoD = n(),
    `AoD Covered` = paste(AoD, collapse = ", ")
    ) %>%
  print
```

```{r join d_course_detail}
d_course <- d_course %>%
  left_join(d_ILO_detail       , by = "Course ID") %>%
  left_join(d_assessment_detail, by = "Course ID") %>%
  left_join(d_AoD_detail       , by = "Course ID") %>%
  select(
    `Course ID`, `Course Title`, Cluster,
    n_ILO,
    n_assessment, `Assessments Covered`,
    n_AoD, `AoD Covered`,
    everything()
    ) %>%
  print

rm(d_ILO_detail, d_assessment_detail, d_AoD_detail)
```

The undegraduate research courses (*UGR-*) are only present at the `3000` level (advanced level). Yet, these course are also offered at the `2000` level (intermediate level). We use an `rbind` to duplicate the rows of the course `UGR3000` and mutate their `Code` to `UGR2000`.
```{r create UGR2000}

d_course_UGR_2000 <- d_course %>%
  filter(
    `Course ID` %in% c("UGR3001", "UGR3002", "UGR3003", "UGR3005")
    ) %>%
  mutate(
    `Course ID` = case_when(
      `Course ID` == "UGR3001" ~ "UGR2001",
      `Course ID` == "UGR3002" ~ "UGR2002",
      `Course ID` == "UGR3003" ~ "UGR2003",
      `Course ID` == "UGR3005" ~ "UGR2005"
      )
    ) %>%
  print

d_course <- d_course %>%
  rbind(
    d_course_UGR_2000
    )

print(
  d_course %>%
    filter(
      str_detect(`Course ID`, "UGR")
      )
  )

rm(d_course_UGR_2000)
```

Finally, we add a series of informative variable at the course level.
```{r d_course additional info}
d_course <- d_course %>%
  separate(
    col     = `Course ID`,
    into    = c("Letters", "Number"),
    sep     = 3,
    remove  = FALSE,
    convert = TRUE
    ) %>%
  mutate(
    Level   = case_when(
      between(Number, 1000, 1999) ~ "Introductory",
      between(Number, 2000, 2999) ~ "Intermediate",
      between(Number, 3000, 3999) ~ "Advanced"    )
    ) %>%
  select(`Course ID`, Letters, Number, Level, everything()
    ) %>%
  print
```

@@

```{r extracting overview, cache = TRUE}
#
# Set up
years <- c("2014-2015", "2015-2016", "2016-2017", "2017-2018", "2018-2019")

headers <- c(
  "^Core Courses \\(COR\\)",
  "^Humanities \\(HUM\\)",
  "^Sciences \\(SCI\\)",
  "^Social Sciences \\(SSC\\)",
  "^Skills Trainings? \\(SKI\\)",
  "^Projects? \\(PRO\\)",
  "^Undergraduate Research", "UCM Undergraduate\r\nResearch", "UCM Undergraduate\r\n  Research",
  "Appendix"
  ) %>%
  paste(collapse = "|")

overview_start <- c(
  "COR",
  "HUM", "SCI", "SSC", 
  "SKI", "PRO",
  "UGR", "CAP"
  ) %>% 
  paste(collapse = "|")

is_start_overview_section  <- function(string) string %>% str_detect(pattern = "^Core Courses \\(COR\\)")
is_end_overview_section    <- function(string) string %>% str_detect(pattern = "Appendix")
is_header                  <- function(string) string %>% str_detect(pattern = headers)

extract_code               <- function(string) string %>% str_sub(start = 1, end = 7)
is_overview_start          <- function(string) string %>% extract_code %>% str_detect(pattern = overview_start)
paste_if_two_page_overview <- function(page, page_following){

  # if the page is the start of an overview,
  if(page %>% is_overview_start){

    # then, if the following page is also the start of an overview, the overview is simply the current page
    if(page_following %>% is_overview_start | is.na(page_following)){

      page

    # if the following page is also the start of an overview, the overview spans over the current and the following page
    }else{

    paste(page, page_following)

    }

  # if the page is not the start of an overview, return an NA
  }else{

    NA_character_

  }

}

#
# Loop

for(i in seq_along(d_text$catalogues)){

  catalogue_all <- d_text$catalogues %>%

    # extract catalogue from corpus
    .[[i]] %>%
    content %>%

    # create a tibble
    tibble(
      page = .
      ) %>%

    # identify start and end of overview section of catalogue
    mutate(
      page_n                    = row_number(), 
      is_start_overview_section = page %>% is_start_overview_section,
      is_end_overview_section   = page %>% is_end_overview_section
      )

  # Check that there is one and only one is_start_overview_section and no more than 1 is_end_overview_section.
  if(sum(catalogue_all$is_start_overview_section) == 0) print("error: no overview_section_start"      )
  if(sum(catalogue_all$is_start_overview_section) >  1) print("error: multiple overview_section_start")
  if(sum(catalogue_all$is_end_overview_section  ) >  1) print("error: multiple overview_section_end"  )

  # Extract overview section from catalogue
  catalogue_overview <- catalogue_all %>%

    # identify and filter the pages that are in the overview section (is_overview_section)  
    mutate(
      is_after_start_overview_section = cumany( is_start_overview_section),
      is_before_end_overview_section  = cumall(!is_end_overview_section  ),
      is_overview_section             = is_after_start_overview_section & is_before_end_overview_section
      ) %>%

    filter(
      is_overview_section
      ) %>%

    # exlude headers (is_to_exclude) as well as the first and the last page 
    filter(
      ! page %>% is_header
      ) %>%

    select(
      - c(
        is_start_overview_section, is_end_overview_section,
        is_after_start_overview_section, is_before_end_overview_section,
        is_overview_section
        )
      )

  d_text$overview[[i]] <- catalogue_overview %>%
    transmute(
      text          = list(page, lead(page)) %>% pmap_chr(paste_if_two_page_overview),
      `Course ID` = text %>% extract_code,
      year          = years[i]
    )

}

d_text <- d_text[c("overview", "manuals")]
d_text$overview <- bind_rows(d_text$overview)

rm(
  is_end_overview_section, is_header, is_overview_start, is_start_overview_section, paste_if_two_page_overview,
  headers, i, overview_start, years,
  catalogue_all, catalogue_overview
  )
```

@@

Since we want to use tools from dplyr and tidytext we must first transform our corpus into a dataframe.
```{r d_manual}
d_text$manuals <- d_text$manuals %>%
  tidy %>%
  select(
    id, text
    ) %>%
  mutate(
    `Course ID` = id %>% extract_code
    ) %>%
  select(
    -id
    ) %>%
  print
```

@@

To put everything into tidy text format, we first create three tibbles `d_overview_tidy`, `d_description_tidy`, `d_manual` that respectively store the overviews, descriptions and text from manuals in the tidy text format, with one row per course-year-word (and course-word for `d_manual`).
```{r tidy d_description}
tidy_text <- function(df){

  df %>%
    unnest_tokens(
      output = word,
      input  = text
      )

}

d_text <- d_text %>% map(tidy_text)
```

@@

We first create a function `stem_hunspell` which, given a term, returns its most basic stem (the last one from the list of stem returned by `hunspell_stem`). We would like to apply `stem_hunspell` on the words of `d_overview_tidy` and `d_manual`, since they have similar structures, we row bind them into `dictionary` to ease the application of `stem_hunspell`. However, since, `stem_hunspell` is not a vectorized function and the number of words in `dictionary` is large, we first use distinct on the `word` variable to find a list containing *once* each term present in the course overviews and manuals. Then, we use `mutate` to apply the function `stem_hunspell` on each word from our dictionary and save its results as a new column `word_stem`.
```{r stemming dictionary, cache = TRUE}
stem_hunspell <- function(term) {

  stems   <- hunspell_stem(term)[[1]] # look up the term in the dictionary

  n_stems <- length(stems)            # number of stems

  if (n_stems == 0) term              # if no stems, return original term
  else              stems[[n_stems]]  # if multiple stems, return last (most basic) stem

}

dictionary <- d_text$overview$word %>%
  union(
    d_text$manuals$word
    ) %>%
  tibble(
    word = .
    ) %>%
  mutate(
    word_stem = word %>% map_chr(stem_hunspell)
    )

# TODO: "destem" terms by hand: cuss => discuss
filter(dictionary, word_stem == "cuss")

@@

Then, we use `stem_with_dictionary` to include the stems of all words in `d_description`, `d_overview`, and `d_manual`.
```{r stemming data sets}
stem_with_dictionary <- function(data){

  data %>%
    left_join(
      dictionary,
      by = "word"
      ) %>%
    rename(
      word_original = word,
      word          = word_stem
      )

}

d_text <- d_text %>% map(stem_with_dictionary)

rm(stem_hunspell, stem_with_dictionary)
```

### Removing Stopwords
Finally, we want to filter out some uninformative words from our textual data. For this, we first store all the unwanted words in a vector `sw_owm`. We also create function `remove_sw` which receives a dataframe as input and filters out all words in `sw_own`. Then we apply this function to `d_description`, `d_overview`, and `d_manual`.
```{r}
# Own stop words
sw_own <- tibble(
    word = c(
      as.character(1 : 1e3)
      )
    )

remove_sw <- function(data){

  data %>%
    anti_join(
      stop_words,
      by = "word"
      ) %>%
    anti_join(
      sw_own,
      by = "word"
      )

}

d_text <- d_text %>% 
  map(remove_sw) %>% 
  print

rm(sw_own, remove_sw)
```

@@

# Save Data
```{r}
save(d_course, lists, d_AoD, d_assessment, d_ILO,
     file = "Output/data_general.RDATA")
save(d_transcript,
     file = "Output/data_pillar_1.RDATA")
save(d_text,
     file = "Output/data_pillar_2.RDATA")
```

# Extra

## Extracting Descriptions

```{r extracting description, eval = FALSE}
